---
title: "COMPSCIX 415.2 Homework 2"
author: "Andrew Wong"
date: "February 5, 2019"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
```

#3.2.4

## **1)**
```{r}
ggplot(data = mpg)
```

ggplot(ata = mpg) creates a blank screen.

## **2)**
```{r}
dim(mpg)
```

mpg has 234 rows and 11 variables

## **3)**

drv describes whether a car is front, rear, or all-wheel drive.

## **4)**
```{r}
ggplot(data = mpg, mapping = aes(x = hwy, y = cyl)) + geom_point()
```

## **5)**
```{r}
ggplot(data = mpg, mapping = aes(x = class, y = drv)) + geom_point()
```

The plot uses two categories as parameters. 

#3.3.1

## **1)**
In order to change the points blue, the color designation must be placed outside of 'aes'.

## **2)**
manufacturer model, year, trans, drv, fl, and class are categorical.

displ, cty, cyl, and hwy are continuous.

## **3)**
```{r}
ggplot(data = mpg, mapping = aes(x = drv, y = displ, color = hwy)) + geom_point()

ggplot(data = mpg, mapping = aes(x = drv, y = displ, size = hwy)) + geom_point()

#ggplot(data = mpg, mapping = aes(x = drv, y = displ, shape = hwy)) + geom_point() Results in an error stating "A continuous variable can not be mapped to shape"
```
## **4)**
```{r}
ggplot(data = mpg, mapping = aes(x = drv, y = displ, color = trans, shape = trans)) + geom_point()
```

## **5)**
If a plot uses shapes, stroke will alter the border of them.

## **6)**
```{r}
ggplot(data = mpg, mapping = aes(x = hwy, y = cyl, color = displ < 5)) + geom_point()
```

If an aesthetic is mapped to something other than a variable, the plot will indicate which points meet the conditions under the aesthetic.

#3.5.1

##**4)**
Facetting can better show statistics for a certain subgroup (in this example, the car's class). 
##**5)**

In facet_wrap(), nrow and ncol set the number of columns and rows for a facet respectively.

facet_grid() uses information from variables to determine the number of rows and columns.

#3.6.1
##**1)**
geom_line() will create a line chart, geom_boxplot() creates a boxplot, geom_bar() creates a histogram, and geom_area() will make an area chart.

##**2)**
Prediction: geom_smooth(se = FALSE) will create a trendline along the points where se = FALSE.

```{r}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

Instead the se = FALSE removed geom_smooth()'s confidence interval.
##**3)**

show.legend = FALSE stops the legend from appearing on a graph. Removing it will display a graph with the legend on the side. It was removed from the example because the focus was on the shape of the graphs in question.

##**4)**
se affects the confidence interval for geom_smooth().

##**5)**

The graphs will look the same, if the mapping information would be the same for two different types of plots, it can be put under ggplot.

#3.7.1 Question 2
geom_col() creates a bar graph with x and y axes provided by the user. geom_bar() on the other hand only accepts an x-axis input.