---
title: "COMPSCIX 415.2 Homework 3"
author: "Andrew Wong"
date: "February 18, 2019"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
library(nycflights13)
```
#3.8.1
##**1)**
The points on the plot are overlapping. One way to impove it would be to alter the alpha of the points or use geom_jitter().

##**2)**
geom_jitter() uses hieght and width to determine the spacing between overlapping points.

##**3)**
geom_jitter() affects the spacing between overlapping points. geom_count() affects the proporties of the points.

##**4)**
```{r}
ggplot(data = mpg, mapping = aes(x = drv, y = hwy)) + geom_boxplot()
```

#3.9.1
##**2)**
The labs() function can change the name of various labels such as the title or captions.

##**4)**
According to the plot, a car's city milage directly affects its milage on the highway.

coord_fixed() fixes the ratio between the number of units on the x and y-axes.

geom_abline() creates a line with the slope of the plot.

#4.4.1
##**1)**

my_variable uses a different "i" than my_variable.

##**2)**
```{r}
#ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy)) has overlapping points
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy), position = "jitter")

#fliter(mpg, cyl = 8) filter is misspelled and "=" needs to be "=="
filter(mpg,cyl == 8)

#filter(diamond, carat > 3) "diamond" is missing an "s"
filter(diamonds, carat > 3)
```


#5.2.4
##**1)**
```{r}
filter(flights, arr_delay >= 120)

filter(flights, dest == "IAH" | dest == "HOU")

filter(flights, carrier %in% c("AA", "UA", "DL"))

filter(flights, month %in% c(7, 8, 9))

filter(flights, dep_delay == 0 & arr_delay < 120)

filter(flights, dep_delay - arr_delay <= 30)

filter(flights, dep_time <= 600)
```

##**3)**
```{r}
filter(flights, is.na(dep_time) == TRUE)
```

8255 flights don't have dep_time. Other missing variables are dep_delay, arr_time, arr_delay, tailnum, and air_time. These rows represent flights that did not take off.

##**4)**
NA ^ 0 will be one as anything to the 0th power will be one. NA | TRUE looks for entries that match either condition. FALSE & NA will only check for entries that return FALSE and ignore missing entries.

#5.4.1
##**1)**
```{r}
select(flights, dep_time, dep_delay, arr_time, arr_delay)

flights %>% select(dep_time, dep_delay, arr_time, arr_delay)
```
##**3)**
one_of() tries to match strings with variables in a givin data set. If one of the characters in "vars" is not a variable in the data base, R will return a warning and still execute using one_of().