---
title: "COMPSCIX 415.2 Homework 4"
author: "Andrew Wong"
date: "February 25, 2019"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
library(nycflights13)
```

#5.6.7
##**2)**
```{r}
not_cancelled <- flights %>% filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% group_by(dest) %>% summarize(n = sum(!is.na(dep_time)))

not_cancelled %>% group_by(tailnum) %>% summarize(n = sum(distance))
```

##**4)**
```{r}
flights %>% group_by(month, day) %>% summarise(prop_cancelled = mean(is.na(dep_time)), avg_delay = mean(dep_delay, na.rm = 'TRUE')) %>% ggplot(mapping = aes(y = prop_cancelled, x = avg_delay)) + geom_point()+ geom_smooth()
```
There appears to be a direct relationship between the average delay and the proportion of flights cancelled.

##**6)**
```{r}
flights %>% count(dep_time)

flights %>% count(dep_time, sort = TRUE)
```
When applied to the count() function, the sort argument organizes the graph by n in descending order.

#10.5
##**1)**
If you print a data.frame, the console will display every row in the data set. Printing a trbble will only show the first 10 rows.

##**2)**
```{r}
df <- data.frame(abc = 1, xyz = "a")
df$x #Even though there is no column named "x", the code will still execute. This could cause problems if you made a mistake.
df[, "xyz"]
df[, c("abc", "xyz")]

dfx <- as_tibble(df)
#dfx$x results in an error as there is no column named "X".
dfx[, "xyz"]
dfx[, c("abc", "xyz")]
```

##**3)**
```{r}
my_var <- "mpg"
car_tib <- as_tibble(mtcars)
mtcars[my_var]
```
##**6)**
```{r}
print(flights, n_extra = 3)#n_extra controls how many extra variables will be printed at the footer.

print(flights, n_extra = 2)#n = 2, therefore the footer will list the next 2 variables of the tibble at the footer.
```

#12.3.3
##**2)**
1999 and 2000 without quotes are considered numbers whereas 1999 and 2000 are considered strings. In order to pull data under 1999 and 2000, the years must be put under quotations marks.

##**3)**
```{r}
 people <- tribble(
   ~name,             ~key,    ~value,
   #-----------------|--------|------
   "Phillip Woods",   "age",       45,
   "Phillip Woods",   "height",   186,
   "Phillip Woods",   "age",       50,
   "Jessica Cordero", "age",       37,
   "Jessica Cordero", "height",   156
 )
#spread() will result in an error as Phillip has duplicate entries under "age"

 people <- tribble(
    ~name,             ~key,    ~value, ~obs,
    #-----------------|--------|-------|-----
    "Phillip Woods",   "age",       45,  1,
    "Phillip Woods",   "height",   186,  1,
    "Phillip Woods",   "age",       50,  2,
    "Jessica Cordero", "age",       37,  1,
    "Jessica Cordero", "height",   156,  1
  )#The obs column ensures the two age entries unique
 people %>% spread(key, value)
```

##**4)**
```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)
```
The variables for this data set are: gender(male or female), pregnant (yes or no), and how many ( responses for either yes or no)
```{r}
preg %>% gather(male, female, key = "gender", value = "how many")
```

#12.4.3
##**1)**
```{r}
y <- tibble(x = c("a,b,c", "d,e,f,g", "h,i,j"))
y %>% separate(x, c("one", "two", "three"))
y %>% separate(x, c("one", "two", "three"), extra = "merge")#extra tells R what to do when a row has too many pieces. In this case, any extra pieces a row has will be combined into a single piece in the last column.

z <-  tibble(x = c("a,b,c", "d,e", "f,g,i"))
z %>% separate(x, c("one", "two", "three"))
z %>% separate(x, c("one", "two", "three"), fill = "right")#fill tells R what to do when a row doesn't have enought peice. In this case, it will insert an NA on the far right column.
```

##**2)**
```{r}
z %>% separate(x, c("one", "two", "three"), fill = "right", remove = FALSE)#The remove argument, set as TRUE by default, stops separate from displaying the original tibble as part of the output. 

s <- z %>% separate(x, c("one", "two", "three"), fill = "right")
s %>% unite("2/3", two, three, sep = ' ', remove = FALSE)#remove is set to TRUE by default which does not output the columns that were combined.
```


#Addidtional Question
```{r}
baby_data <- read_delim('C:/Users/Andy/Downloads/baby_names.txt', delim = '|')
glimpse(baby_data)
write_csv(baby_data, 'C:/Users/Andy/Documents/baby_names.csv')
baby_data2 <- read_csv('C:/Users/Andy/Documents/baby_names.csv')
glimpse(baby_data2)
```

