---
title: "Homework 9/Final"
author: "Andrew Wong"
date: "April 4, 2019"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
library(broom)
```

#Exercise 1

##Step 1
```{r}
samp_fun <- function(samp_size, samp_rate) {
  
  samp <- rexp(n = samp_size, rate = samp_rate)
  
  samp_avg <-  mean(samp)
  
  samp_std_dev <- sd(samp)
  
  stats <- list(samp_avg = samp_avg, samp_std_dev = samp_std_dev)
  return(stats)
}
```

##Step 2
```{r}
sample_means <- rep(NA, 1000)

sample_sds <- rep(NA, 1000)

for (i in 1:1000) {
  
  samp_run <- samp_fun(50, 1/10000)
  
  sample_means[i] <- samp_run$samp_avg
  
  sample_sds[i] <- samp_run$samp_std_dev
  
}

sample_stat <- list(samp_mean = sample_means, samp_sd = sample_sds)
```
##Step 3
```{r}
mean_plot <- as_tibble(sample_stat) %>% ggplot() + geom_histogram(aes(samp_mean))

mean_plot

sd(sample_stat$samp_mean)

theo_error <- 10000/sqrt(50)

theo_error

mean_sd <- mean(sample_stat$samp_sd)

mean_sd


```

##Step 4
```{r}
sample_means2 <- rep(NA, 1000)

sample_sds2 <- rep(NA, 1000)

for (i in 1:1000) {
  
  samp_run2 <- samp_fun(5000, 1/10000)
  
  sample_means2[i] <- samp_run2$samp_avg
  
  sample_sds2[i] <- samp_run2$samp_std_dev
  
}

sample_stat2 <- list(samp_mean2 = sample_means2, samp_sd2 = sample_sds2)

mean_plot2 <- as_tibble(sample_stat2) %>% ggplot() + geom_histogram(aes(samp_mean2))

mean_plot2

sd(sample_stat2$samp_mean2)

theo_error <- 10000/sqrt(5000)

theo_error

mean_sd2 <- mean(sample_stat2$samp_sd2)

mean_sd2
```

#Exercise 2

```{r}
choochoo <- read_delim('C:/Users/andy/documents/train.csv', delim = ',')

train_reg <- lm(formula = SalePrice ~ LotArea + OverallQual + ExterQual, data = choochoo)

glance(train_reg)$r.squared

train_reg
```

##Interpret the coefficient on LotArea
The price of the Lot increases by $1.45 per square foot.

##Interpret the coefficient on ExterQualGd
The difference in price between "Poor" areas and "Good" areas is -$71529.49. A "Good" area is more expensive than a "Poor" one.

##Compare this model to the model we fit in HW 7 with GrLivArea, OverallQual, Neighborhood. Which is the better fitting model?
```{r}
train_lm <- lm(formula = SalePrice ~ GrLivArea + OverallQual + Neighborhood, data = choochoo)#regression from HW 7

glance(train_lm)$r.squared

glance(train_reg)$r.squared
```

The HW 7 model has a higher R squared and therefore is better fit.

#Exercise 3
```{r}
test_dat <- read_delim('C:/Users/andy/dropbox/ab_test_data.csv', delim = ',')
```

##a. What proportion of visitors converted for each version of the webpage?
```{r}
test_dat_a <- test_dat %>% filter(version == 'A')

prop_a <- mean(test_dat_a$conversion, na.rm = TRUE)

test_dat_b <- test_dat %>% filter(version == 'B')

prop_b <- mean(test_dat_a$conversion, na.rm = TRUE)

prop_a
prop_b
```

##b. Perform the AB test in R. What is the p-value for the AB test (hypothesis test of proportions)?
```{r}
size_a <- count(test_dat_a)$n #count() returns a tibble with one column named "n"
size_b <- count(test_dat_b)$n

samp_a <- rbinom(n = 1, size = size_a, prob = prop_a)
samp_b <- rbinom(n = 1, size = size_b, prob = prop_b)

prop_test_ab <- prop.test(c(samp_a, samp_b), c(size_a, size_b))
prop_test_ab$p.value
```


