---
title: "Homework 7"
author: "Andrew Wong"
date: "March 18, 2019"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(mdsr)
library(broom)
```

#Exercise 1
```{r}
choochoo <- read_delim('C:/Users/andy/documents/train.csv', delim = ',')
glimpse(choochoo)
```
The train data set has 81 columns and 1460 observations

#Exercise 2
```{r}
choochoo %>% ggplot(aes(SalePrice)) + geom_histogram()

choochoo %>% ggplot(aes(Neighborhood, SalePrice)) + geom_col() + coord_flip()

choochoo %>% ggplot(aes(OverallQual, SalePrice)) + geom_col()
```

#Exercise 3
```{r}
mean(choochoo$SalePrice)

SalePrice_Reg_Solo <- lm(formula = SalePrice ~ 1, data = choochoo)

SalePrice_Reg_Solo

glance(SalePrice_Reg_Solo)
```

#Exercise 4
```{r}
train_lm <- lm(formula = SalePrice ~ GrLivArea + OverallQual + Neighborhood, data = choochoo)

train_lm
```
##How would you interpret the coefficients on GrLivArea and OverallQual?
As the ground area increases, the sale price increases by $55.56. As the overall quality increases, the sale price increases by $20951.42.

##How would you interpret the coefficient on NeighborhoodBrkSide?
The more locations in Brookside there are, the lower the sale price will be.

##Are the features significant?
```{r}
tidy(train_lm)
```
Yes, the p-values are all under .05.

##Are the features practically significant?
Yes, the features make realistic sense.

##Is the model a good fit?
The model is a good fit.

#Exercise 5
```{r}
 lm(formula = SalePrice ~ LotConfig, data = choochoo)

 lm(formula = SalePrice ~ MSZoning, data = choochoo)
 
 lm(formula = SalePrice ~ LotShape, data = choochoo)
```


#Exercise 6
```{r}
sim1a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)


sim2a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)


sim3a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)


sim4a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)


sim5a <- tibble(
  x = rep(1:10, each = 3),
  y = x * 1.5 + 6 + rt(length(x), df = 2)
)

sim1a_lm <- lm(x~y,sim1a)

sim2a_lm <- lm(x~y,sim2a)

sim3a_lm <- lm(x~y,sim3a)

sim4a_lm <- lm(x~y,sim4a)

sim5a_lm <- lm(x~y,sim5a)

sim1a_lm
glance(sim1a_lm)

sim2a_lm
glance(sim2a_lm)

sim3a_lm
glance(sim3a_lm)

sim4a_lm
glance(sim4a_lm)

sim5a_lm
glance(sim5a_lm)
```

The Coefficients and R squared are all within a certain range but there's no discernable pattern.